{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-03-12 documents/fluorescence.tex
fucker
I keep re-writing things but they don't get any better!
Text and prop improvements
Tersenating
Rewording text slightly in case biorxiv is a good idea

@@

\subsection{Light source}

@@

@@

@@

Silicon photomultipliers like ON's C-Series are almost certainly sufficient for this application, eliminating the HV requirements of PMTs at the cost of a higher dark count and slightly smaller active area.

@@

Another neat technique is to add

>>>>

the base had integral overcurrent protection, which was triggered a few times during development - a very useful

@@

Unlike luminescence techniques,

%\subsubsection{Light source}

@@

it has been noted that water is a good fluorescence quencher and that this might be how

@@

The fiber optic \cite{vurek1982nanoliter}

@@

Silicon photomultipliers like ON's C-Series are almost certainly sufficient for this application, eliminating the HV requirements of PMTs at the cost of a smaller active area.

@@

Another neat technique is to add I/Q

### 2021-03-12 documents/summary.tex
Rewording text slightly in case biorxiv is a good idea

A few well-established non-resonant non-thermal effects caused by extreme electric fields have already been put to practical use. Electroporation\cite{Electroporation1988}, now a common laboratory procedure, occurs when an enormous electric field causes ions in solution to diffuse across a cell membrane, capacitively charging it. This leads to a change in lipid conformation, reversibly rendering the membrane permeable (among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's understanding\cite{Theoretical2007}).

Therapies based on irreversible electroporation\cite{Nonthermal2013}\cite{Lipid2017} have recently been used in the clinic\cite{Irreversible2013} for tumor ablation. There is much discussion on electroporation as an alternative to viral vectors, but we have not yet found any discussion of clinical treatment of viral infection with these conventional electroporation therapies.% In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.

@@

@@

	\item Infrared thermography only determines the surface temperature. Based on heating patterns seen in other experiments\cite{Effects1950}, the observed surface temperature rise does not seem to conclusively rule out a very localized thermal effect. 
	\item Therefore, without free-space dosimetry or simulation of power density, the frequency-selective inactivation could possibly be explained by the frequency response of the power amplifier, antenna gain, and absorption of the cuvette.
\end{itemize}

\footnote{It is interesting to consider that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of stringent peer review, could unintentionally tend towards a literature populated with only the most abstruse and difficult to explain false-positive results.}

@@

An approximate charge distribution of the proteins of the virion can be obtained by multiplying primary structure charges (in our case, extracted \cite{CIDER2017}, or (\cite{complete2003})) by observed protein contribution to total MW\cite{Quantitative1981}, old 2D-PAGE gels \cite{Influenza1978}\cite{Structurea} (which also provides an estimate of the variation in the charge, important for accurate spectroscopy, see supplemental) - or perhaps directly via extraction from whole-virion CryoEM maps, enabled by the charge-sensitive nature of the technique \cite{Identification2018}\cite{Electrostatic2020}. This has not yet been implemented in any software tools and seems quite tricky.

The genome charge is almost entirely neutralized by the nucleocapsid.

@@

Non-resonant capsid and envelope breakage with 120 pulses, 500 ns each, at 3 MV/m, has been previously observed\cite{Inactivation1990} but the RNA damage suggests that this is an electrochemical artifact \cite{Formation1996} (and \cite{Microwave1987}). Long pulses at $10$ MV/m electroporate enveloped viruses similarly to host cells\cite{AC2017} but do not necessarily affect T4\cite{Manipulation2013}.

@@

Previous field limits were set by the microwave hearing effect, a primarily thermoelastic mechanical \cite{MICROWAVEINDUCED1975}. Thermoelastic effects can cause damage, but primarily when \cite{Thermoacoustic2017}\cite{MECHANICAL1968}. \cite{Radiation1996}

There is a body of work on coherent control of viral inactivation using picosecond laser exposure \cite{Maximum2010}; targeting small proteins seems to require very large fields\cite{Picosecond2016b}, but breaking viral capsids by exciting long-wavelength vibrations using Raman scattering has been reported experimentally \cite{Inactivation2007}\cite{Prospects2012}\cite{Studies2014}, however these results have failed replication\cite{No2011}. The author has not investigated this mechanism in any detail. Molecular dynamics of ISRU has been considered \cite{Maximum2010}, (\cite{Vibrational2009} but without considering heat-bath damping). Interestingly, if the well-established 1 TW power density\cite{Targeted2002} for mammalian cell damage by femtosecond laser is scaled linearly with time to the nanosecond regime, a power density similar to that of \cite{Repeated2020} is found ($1\ \text{TW/m}^2 / (100\ \text{ps} / 0.3\ \text{ps}) = 3\ \text{GW/m}^2$).

@@

Positive artifacts are very common in this field, and extreme care in experimental design appears to be required to produce any meaningful result. Excellent best-practices guidelines and meta-analyses are available in \cite{Biological2016} \cite{Comprehensive2018} \cite{Funding2019}, \cite{chou1996radio} and \cite{Effects2016}.

@@

\subsection{Experiment methods}

>>>>

A few well-established non-resonant non-thermal effects caused by extreme electric fields have already been put to practical use. Electroporation\cite{Electroporation1988}, now a common laboratory procedure, occurs when an enormous electric field causes ions in solution to diffuse across a cell membrane, capacitively charging it. This leads to a change in lipid conformation, reversibly rendering the membrane permeable. This is one among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's current understanding\cite{Theoretical2007}.

Therapies based on irreversible electroporation\cite{Nonthermal2013}\cite{Lipid2017} have recently been used in the clinic\cite{Irreversible2013} for tumor ablation. There is much discussion on electroporation as an alternative to viral vectors, but we have found surprisingly little discussion on clinical treatment of viral infection with these conventional electroporation therapies.% In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.

Long pulses at $\approx10$ MV/m appear to electroporate enveloped viruses similarly to host cells\cite{AC2017}, which we believe might hint that a regime of intensity, duration, and pulse count may exist to target the viral envelope. The same field intensity does not appear to damage phages with protein capsids\cite{Manipulation2013}.

Non-resonant capsid and envelope breakage with 120 pulses, 500 ns each, at 3 MV/m, has been previously observed\cite{Inactivation1990}, but the RNA damage suggests that this is an electrochemical artifact \cite{Formation1996} (c.f. \cite{Microwave1987}).

@@

However, perhaps regrettably, the experiments reported here were not designed to address the question of whether conventional ion- and bilayer- driven electroporation can be harnessed, but rather to test whether purely mechanical damage from $qE$ forces can be easily observed.

@@

	\item Infrared thermography only determines the surface temperature. Based on heating patterns seen in other experiments\cite{Effects1950}, the observed surface temperature rise does not perhaps conclusively rule out a very localized thermal effect. 
	\item Therefore, without free-space dosimetry or simulation of power density, the frequency-selective inactivation could possibly be explained by the frequency response of the power amplifier, antenna gain, and absorption of the cuvette.
\end{itemize}

\footnote{It is interesting to consider that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of stringent peer review, could unintentionally tend towards a literature populated with only the most abstruse and difficult to explain false-positive results. We do not suggest that this is relevant in this case; but a cursory review of the papers cited in that excellent meta-analysis leads both very difficult to find fault in, and entirely disproved by later research.}

@@

An approximate upper bound on the charge distribution due to the proteins of the virion can be obtained by multiplying primary structure charges (in our case, extracted \cite{CIDER2017}, or (\cite{complete2003})) by observed protein contribution to total MW\cite{Quantitative1981}, old 2D-PAGE gels \cite{Influenza1978}\cite{Structurea} (which also provides an estimate of the variation in the charge, important for accurate spectroscopy). See supplemental data. It appears that the genome charge is largely neutralized by the nucleocapsid.

It might be possible to extract the charge directly from whole-virion CryoEM maps, enabled by the charge-sensitive nature of the technique \cite{Identification2018}\cite{Electrostatic2020}. This has not yet been implemented in any software tools and seems quite tricky.

@@

@@

Previous field limits were generally set by the microwave hearing effect, a primarily thermoelastic mechanical \cite{MICROWAVEINDUCED1975}. Thermoelastic effects can cause damage\cite{MECHANICAL1968}, particularly when susceptors are implanted\cite{Thermoacoustic2017}, but do not seem to be a significant concern in most cases \cite{Radiation1996}.

In general, methods targeting small proteins seem to require impractical fields\cite{Picosecond2016b}. Very recently, a region of the SARS-NCoV-2 spike protein has been reported to be susceptible to electric fields\cite{Receptor2021}; however the field intensity required appears to be on the order of 3 GV/m.

There is a body of work on coherent control of viral inactivation using picosecond laser exposure \cite{Maximum2010}. Breaking viral capsids by exciting long-wavelength vibrations using Raman scattering has been reported experimentally \cite{Inactivation2007}\cite{Prospects2012}\cite{Studies2014}, however these results have failed replication\cite{No2011}. The author has not investigated this mechanism in any detail. Molecular dynamics of ISRU has been considered \cite{Maximum2010}, (\cite{Vibrational2009} but without considering heat-bath damping). Interestingly, if the well-established 1 TW power density\cite{Targeted2002} for mammalian cell damage by femtosecond laser is scaled linearly with time to the nanosecond regime, a power density similar to that of \cite{Repeated2020} is found ($1\ \text{TW/m}^2 / (100\ \text{ps} / 0.3\ \text{ps}) = 3\ \text{GW/m}^2$).

@@

Positive artifacts are very common when exposing organisms to electric fields, and extreme care in experimental design appears to be required to produce any meaningful result. Excellent best-practices guidelines and meta-analyses are available in \cite{Biological2016} \cite{Comprehensive2018} \cite{Funding2019}, \cite{chou1996radio} and \cite{Effects2016}.

@@

\subsection{Materials and methods}
